\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}



\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{bookmark}
\input{glyphtounicode}

% ---------- ATS Optimization ----------
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{5pt}

\usepackage[margin=0.4in]{geometry}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-8pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% ---------- Custom Commands ----------
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{\linewidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, label={$\bullet$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

% -----------------------------------------
%               RESUME START
% -----------------------------------------
\begin{document}

% ---------- Heading ----------
\begin{center}
    {\Huge \textbf{Ayush Mishra}} \\ \vspace{2pt}
    \small Prayagraj, India | +91-8960961976 | \href{mailto:aayumishra2024@gmail.com}{aayumishra2024@gmail.com} \\ \vspace{2pt}
    \small 
    \href{https://www.linkedin.com/in/ayush-mishra-14a608281/}{LinkedIn} | 
    \href{https://github.com/Ayush120704/Ayush120704}{GitHub} | 
    \href{https://leetcode.com/u/ayushmishra12345/}{LeetCode} | 
    \href{https://ayush-portfolio-psi-one.vercel.app/}{Portfolio}
\end{center}
\vspace{-10pt}

% ---------- Summary ----------
\section{Summary}
\vspace{-2pt}
\small{AI/ML Engineer with expertise in deep learning, NLP, and Computer Vision. Specialized in transformer architectures (BERT, ALBERT), multimodal pipelines, and Retrieval-Augmented Generation (RAG) systems. Experienced in model fine-tuning, transfer learning, and deploying AI applications using PyTorch, Hugging Face, and the MERN stack. GATE CSE 2026 qualified.}
\vspace{-2pt}

% ---------- Education ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {United Institute of Technology}{Expected May 2027}
      {Bachelor of Technology (B.Tech) in Computer Science and Engineering -- CGPA: 8.31/10.0}{Prayagraj, India}
    \resumeSubheading
      {New R.S.J Public School}{2020 -- 2022}
      {Class 12th (CBSE): 83.2\% | Class 10th (CBSE): 89.4\%}{Prayagraj, India}
  \resumeSubHeadingListEnd

% ---------- Skills ----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI/ML}{: PyTorch, Hugging Face Transformers, BERT, ALBERT, Fine-Tuning, Transfer Learning, Vector Embeddings} \\
     \textbf{NLP \& CV}{: Cognitive Distortion Detection, Facial Emotion Recognition, DeepFace, OpenCV, Sentence-Transformers} \\
     \textbf{Generative AI}{: RAG, ChromaDB, LLM Integration, Semantic Search, Vector Databases} \\
     \textbf{Languages}{: Python, Java, C, JavaScript, SQL} \\
     \textbf{Web Stack}{: React.js, Node.js, Express.js, FastAPI, MongoDB, Tailwind CSS, Three.js, REST APIs} \\
     \textbf{Core CS}{: DSA, OOP, Operating Systems, Git, GitHub, NumPy, Pandas}
    }}
 \end{itemize}
 \vspace{-8pt}

% ---------- Experience ----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Collab4Good}{Aug 2025 -- Present}
      {Global Innovation Intern}{Remote / Bangkok, Thailand}
      \resumeItemListStart
        \resumeItem{Developed a full-stack MERN application for NGO resource sharing, improving cross-team workflow efficiency across 5 organizations serving 200+ end users.}
        \resumeItem{Engineered responsive React components and RESTful APIs within an international agile team, delivering milestones 2 sprints ahead of schedule and reducing page load times by 40\%.}
      \resumeItemListEnd

    \resumeSubheading
      {United Institute of Technology}{Jul 2024}
      {Software Engineering Summer Trainee}{Prayagraj, India}
      \resumeItemListStart
        \resumeItem{Built a browser-based text editor with session state persistence using localStorage, eliminating data loss across page reloads for 100+ daily active users.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% ---------- Projects ----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{NeuroWell -- Multimodal Emotional Support System} | \emph{Python, PyTorch, BERT, RAG, ChromaDB, OpenCV}}{2025}
      \resumeItemListStart
        \resumeItem{Architected an end-to-end multimodal AI pipeline integrating speech transcripts, facial expression analysis, and text embeddings for real-time emotional support, processing 3 input modalities simultaneously.}
        \resumeItem{Engineered a RAG system with ChromaDB vector embeddings and cosine similarity retrieval to deliver rubric-grounded contextual responses, improving relevance by 35\% over baseline.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Legal Lens -- AI Legal Document Analyzer} | \emph{React, FastAPI, Sentence-Transformers, ChromaDB, Three.js}}{2025}
      \resumeItemListStart
        \resumeItem{Engineered an asynchronous AI agent system scanning legal contracts for high-risk GDPR/HIPAA clause violations in real time using NLP-based text classification and semantic search.}
        \resumeItem{Built a compliance engine with ChromaDB vector database seeded with regulatory standards and a custom scoring model combining cosine similarity with keyword-penalty weighting.}
        \resumeItem{Implemented WebSocket live updates with automatic HTTP-polling fallback and an interactive 3D vector visualizer using Three.js for embedding space exploration.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{AI Interview Coach -- Multimodal Interview Platform} | \emph{React, Node.js, FastAPI, OpenCV, BERT, MongoDB}}{2025}
      \resumeItemListStart
        \resumeItem{Designed a 3-tier microservice architecture (React frontend, Node.js API, Python FastAPI ML backend) delivering real-time multimodal interview evaluation.}
        \resumeItem{Integrated OpenCV facial expression tracking at 1Hz and a fine-tuned BERT model for filler-word detection, achieving 92\% classification accuracy on validation data.}
        \resumeItem{Developed a timestamp-synchronized signal fusion algorithm computing weighted composite confidence scores and an interactive Three.js scrubbing timeline for session review.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% ---------- Achievements ----------
\section{Honors and Achievements}
 \resumeItemListStart
    \resumeItem{\textbf{GATE CSE 2026 Qualified} -- Cleared Graduate Aptitude Test in Engineering for Computer Science.}
    \resumeItem{\textbf{Global Merit Scholar} -- Selected for AIT Bangkok with 90\% merit scholarship among international applicants.}
    \resumeItem{\textbf{Competitive Programming} -- 150+ day LeetCode streak solving advanced DSA problems; active on Codeforces.}
    \resumeItem{\textbf{Leadership} -- Event Head for Enigma College Fest (5,000+ attendees); Core Organizer for UHack Hackathon.}
 \resumeItemListEnd

\end{document}
